---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DynExpData

<!-- badges: start -->
<!-- badges: end -->

The goal of DynExpData is to provide easy data access to the experimental data from the paper "Identifying dynamic shifts to careless and insufficient effort behavior in questionnaire responses; A novel approach and experimental validation".

## Installation

You can install the development version of DynExpData like so:

``` r
# install.packages("devtools")
devtools::install_github("Schmidtpk/DynExpData")
```

## Instructions

The raw data can be found in this github. The different data parts are in this package under data. The simplest way to work with the data is by using the ``pull_data`` function:

```{r genlist}
library(DynExpData)

# load data into list
data.list <- pull_data()

ls(data.list)

```

If you prefer to work with data.frames, the ``gen_df`` function creates those:

```{r gendf}
# generate data.frame (tidyformat)
df <- gen_df(data.list)

head(df)

```

The exported data.frame contains the columns

- id: Participant ID
- j: Participant ID numeric
- iname: Item name (items 6,7,8,9,and, 10 are reverse coded for each factor)
- time: Response time for item
- timerank: Ranked response time in decimal form
- value: Response to item with reverse coded items already reversed  
- i: Item number (iord)
- t: Item presentation number (tord)
- treatment.timing: Position of treatment instructions for conditions 3 and 4
- instr: Specific instructions
- cond: Condition 1 through 4 (1 and 2 are control)
- value.org: Original item response prior to reverse coding

If you want to sample specific data points, the ``pull_data`` functions has arguments for that. You can look at ``?pull_data`` for details.
