---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DynExpData

<!-- badges: start -->
<!-- badges: end -->

The goal of DynExpData is to provide easy data access to the experimental data from the paper "Identifying dynamic shifts to careless and insufficient effort behavior in questionnaire responses; A novel approach and experimental validation".

## Installation

You can install the development version of DynExpData like so:

``` r
%td: install here
```

## Instructions

The raw data can be found in this github. The different data parts are in this package under data. The simplest way to work with the data is by using the ``pull_data`` function:

```{r genlist}
library(DynExpData)

# load data into list
data.list <- pull_data()

ls(data.list)

```

If you prefer to work with data.frames, the ``gen_df`` function creates those:

```{r gendf}
# generate data.frame (tidyformat)
df <- gen_df(data.list)

head(df)

```

If you want to sample specific data points, the pull_data functions has arguments for that. You can look at ``?pull_data`` for details.
